---
tTitle: "Project 1-DATA MINING"
author: "Bidhan Subedi"
date: "9/3/2021"
output: html_document
---
 <font size="16"> Introduction </font><br>
My data set has information about the world heritage sites all around the globe. I got this data set from kaggle (https://www.kaggle.com/ujwalkandi/unesco-world-heritage-sites?select=whc-sites-2019+-+Copy.xls).It was created at 2019 by Ujwal Kandi. <br>
As a quantitative variable I use latitude,longitude,date_inscribed, and as categorical variable i use category,region_en variables. 
<font size="16"> Organizing the data </font><br>
I had some issue with quantitative variables. I have labeled the graphs using main, xlab and ylab. I used # to comment. I have brief detail about the headers through out the project.
```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
df<- read.csv("whc-sites-2019.csv")
```
## 1
```{r message=FALSE, warning=FALSE}
#The mean value of Latitude's values.
mean(df$latitude)
#The standard deviation.
sd(df$latitude)
#Five number summary
summary(df$latitude)
```
## Graphical Display
Below I have different graphical displays. Histogram, box plot and qq plot is presented for latitude variable which is one of the quantitative variable.The main purpose of a qq plot is to assess normality. Histograms might be second-best option (to normal probability plots) for assessing normality. Boxplots main purpose is to show quartiles and outliers, if there are any present.
```{r message=FALSE, warning=FALSE}
hist(df$latitude, main = "Histogram of Latitude values",xlab = "Latitude (sec)",col = "red",)
boxplot(df$latitude, main= "Box plot showing Latitude", xlab= "Quartile", ylab = "latitude")
qqnorm(df$latitude)
qqline(df$latitude, col = "red")
```

There are some outliers below , which is far from the rest of the values. The distribution is negative skewed.

## 2

## Graphical display looking at longitude and latitude and their correlation

```{r message=FALSE, warning=FALSE}
plot(df$latitude, df$longitude)
cor(df$latitude, df$longitude)
```

The correlation coefficient is a measurement of the closeness of association of the points in a scatter plot to a linear regression line based on those points.

## 3

## Table
Below I have frequency table and relative frequency table. It contains different region and the number of world heritages sites in that region.

## Frequency Table

```{r message=FALSE, warning=FALSE}
table(df$region_en)
```

## Relative Frequency Table

```{r message=FALSE, warning=FALSE}
table(df$region_en)/length(df$region_en)
```

## 4

## Two-way table 

Two way table is made below for two categorical variables. Category and region. The table represents how many Cultural, Mixed and Natural heritage sites are in 7 different region.
```{r message=FALSE, warning=FALSE}
two_way_table <- table(df$category,df$region_en)
two_way_table
```

## 5

## Side-By-Side Plot

Here I use a boxplot with one quantitative and other categorical variable to present side-by-side plot. As X-axis represent different category of heritage sites and Y-axis represent establisment date of the heritage sites.

```{r message=FALSE, warning=FALSE}
boxplot(df$date_inscribed ~ df$category, col="orange", main="Date Inscribed of distributed Category", ylab="Inscribed Date", xlab="Category") 
```

## 6

# BarPlot

One quantative variable is used for making barplot below. Latitude of heritage sites.

```{r message=FALSE, warning=FALSE}
barplot(df$latitude,  main = "Latitude Chart", xlab = "", ylab = "latitude")
```

## Scatter Plot of Longitude Value

```{r message=FALSE, warning=FALSE}
scatter.smooth(df$longitude, main = "Scatter Plot")
```

## HEAT MAP

```{r message=FALSE, warning=FALSE}
data <- read.csv("whc-sites-2019.csv", header = TRUE)
data <- data.matrix(data[,-1])
library(RColorBrewer)
heatmap(t(data),
        main = "Heat Map",
        Rowv = NA,
        Colv = NA,
        col = colorRampPalette(brewer.pal(8, "PiYG"))(25),
        scale = "column")
```
<font size="16"> Conclusion </font><br>
The most interesting feature of my data, graphical analysis of the data. We can predict how  different variables are depending on each other through plotting graphs. As this is my first time exploring data and analyzing in RStudio, I got alot of ideas about how we can manipulate data according to our need. 
<br>
